calibration

### 2016-04-05 Rmd/calibration.Rmd
changes to space-time.Rmd: 1. rules and code for perturbing uncertain variables replaced in favor of uncertainty analysis on 4 main variables for all records. 2. mean features values for calibration data merged with main dataset 3. 2 resampling/bootstrap variants run and plotted: 1.  perturbation of 4 main variables; 2. bootstrapping with replacement. 4. Main figure made on merged calibration/main dataset made. 5. Additional analyses appears towards end: a) code for calculating percent of records within different portions of space-time domain (still to be made); b) assessment of percentage of

```{r}
# external fixes and recodes, bring back in
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationf.xlsx")))
cal <- data.table(read_excel(fp(p_dat, "merged_calibrationff.xlsx")))
names(cal)
cal[, c("notes", "V29") := NULL]
for(j in names(cal)[c(4:5, 10:24)]) {
  set(cal, j = j, value = as.numeric(cal[[j]]))
}
# length(which(is.na(cal$feature)))

@@

### By feature (individual records) across DOIs
```{r, results='hold'}
CV <- function(x) sd(x) / mean(x)
rnms <- c("DOI", "feature", "observer", "plot_res", "n_sites", "t_btwn_samp",
          "study_duration")
calr <- cal[, rnms, with = FALSE]
# calr[feature != 99, ]
# calr[feature != 99, lapply(.SD, mean), by = .(DOI, feature), 
#      .SDcols = rnms[4:7]]
# calr[feature != 99, .N, by = .(DOI, feature)]
calr[feature != 99, lapply(.SD, CV), by = .(DOI, feature), 
     .SDcols = rnms[4:7]][, lapply(.SD, mean, na.rm = TRUE), 
                          .SDcols = rnms[4:7]]

>>>>

```{r, warning = FALSE}
# external fixes and recodes, bring back in
# cal <- data.table(read_excel(fp(p_dat, "merged_calibrationf.xlsx")))
cal <- data.table(read_excel(fp(p_dat, "merged_calibrationff.xlsx")))
names(cal)
cal[, c("notes", "V29") := NULL]
for(j in names(cal)[c(4:5, 10:24)]) {
  set(cal, j = j, value = as.numeric(cal[[j]]))
}
# length(which(is.na(cal$feature)))

@@

### By feature (individual records) across DOIs
```{r, results='hold'}
CV <- function(x) sd(x) / mean(x)
rnms <- c("DOI", "feature", "observer", "plot_res", "n_sites", 
          "sampled_area", "t_btwn_samp", "study_duration")
calr <- cal[, rnms, with = FALSE]
# calr[feature != 99, ]
# calr[feature != 99, lapply(.SD, mean), by = .(DOI, feature), 
#      .SDcols = rnms[4:7]]
# calr[feature != 99, .N, by = .(DOI, feature)]
calr[feature != 99, lapply(.SD, CV), by = .(DOI, feature), 
     .SDcols = rnms[4:8]][, lapply(.SD, mean, na.rm = TRUE), 
                          .SDcols = rnms[4:8]]
